\cvsection{Experience}
\begin{cventries}
  \cventry
    {Member of Technical Staff Intern}
    {Nutanix}
    {Bangalore, India}
    {May 2017 - Jul. 2017}
    {
      \begin{cvitems}
      \item {Designed a config based python framework to automate the benchmarking of metrics like CPU and memory usage, throughput rate for \textbf{Apache Kafka} through \textbf{JMX beans} and \textbf{confluent-kafka-python} module}
        \item {Built a library module to interact with Kafka in terms of message communication through different modes using the confluent-kafka-python module. Also supported management functionality like CRUD operations over topics, safe removal operations over nodes and topics partition rearrangement operations over a cluster}
        \item {Implemented bulk and stream APIs for reading data from Kafka via different modes using websockets}
        \item {Received a pre-placement offer at the end of the internship period}
      \end{cvitems}
    }
  \cventry
    {Developer Intern}
    {Elanic}
    {Bangalore, India}
    {May. 2016 - Jul. 2016}
    {
      \begin{cvitems}
      \item {Built a \textbf{node.js} module to support atomic transactions in \textbf{MongoDB} including features like savepoint, commit, rollback by extending \textbf{Mongoose}. Used \textbf{Redis}, as in-memory database, to implement functionality of redo logs in Oracle, ensuring atomicity and isolation. Supported some validation checks for partial consistency}
      \item {Built a \textbf{Restify.js} based back-end for Barcode app and designed a website for Elanic Premiere League}
      \end{cvitems}
    }
  \cventry
    {Teaching Assistant}
    {Indian Institute of Technology Kanpur}
    {Kanpur, India}
    {Aug. 2017 - Nov. 2017}
    {
      \begin{cvitems}
        \item {Teaching assistant for the course Data Structures and Algorithms under Prof. Sumit Ganguly}
        \item {Involved in assisting the professor in creating and evaluating assignments, exams for a class of 230 students}
      \end{cvitems} 
    }
\end{cventries}
