\cvsection{Projects}
\begin{cventries}
  \cventry
    {Computer Networks, Prof. Dheeraj Sanghi}
    {\href{https://bitbucket.org/arhamchopra11/decentralized_file_storage}{Decentralized File Storage System}}
    {IIT Kanpur}
    {Oct. 2017 - Nov. 2017}
    {
      \begin{cvitems}
        \item {Designed a decentralized storage system that uses client supplied space to store information in a distributed fashion}
        \item {Designed an application layer protocol for communication with clients via upload, download, and copy requests}
        \item {Implemented replication (via copy functionality) during upload to increase availability of data and prevent data loss}
        \item {Added support for addition new client, and authentication for access control of files for the differnt clients}
      \end{cvitems}
    }
  \cventry
    {Probabilistic Machine Learning, Prof. Piyush Rai}
    {\href{https://bitbucket.org/arhamchopra11/non-parametric-bayesian}{Small Variance Asymptotics}}
    {IIT Kanpur}
    {Aug. 2017 - Nov. 2017}
    {
      \begin{cvitems}
        \item {Studied a subset of \textbf{non parametric bayesian techniques} which are based on \textbf{dirichlet process} and its variants.}
        \item {Studied different sampling-based inference techniques used in extracting data from them such as Gibbs Sampling, Metropolis Hastings, etc. and real-life interpretations like the Chinese Restaurant Process, and the Indian Buffet Process.}
        \item {Studied \textbf{small variance asymptotics}, used to achieve the inference speed of parametric techniques while retaining features from the non-parametric domain. Implemented some of these techniques in python on toy datasets}
      \end{cvitems}
    }
  \cventry
    {Compiler Design, Prof. Amey Karkare}
    {\href{https://bitbucket.org/arhamchopra11/almost-c-compiler}{Almost-C-Compiler}}
    {IIT Kanpur}
    {Jan. 2017 - May 2017}
    {
      \begin{cvitems}
        \item {Implemented minimal features of a \textbf{C Compiler} targeting the \textbf{MIPS Architecture} using the python framework \textbf{PLY}. Tested the correctness of generated code MIPS assembly code for programs like quicksort, ackermann, mergesort, etc.}
        \item {Added support for some non-trivial features like \textbf{type-checking, type-casting of variables, global and local multidimensional arrays, pointers and standard I/O} with terminal}
      \end{cvitems}
    }
  \cventry
    {Computer Systems Security, Prof. Sandeep Shukla}
    {Finding Security Flaws in Zoobar Webserver}
    {IIT Kanpur}
    {Jan. 2017 - May 2017}
    {
      \begin{cvitems}
        \item {Explored the security flaws like control hijacking, privilege separation for Zoobar Web server in a series of assignments}
        \item {Performed simple attacks like buffer overflow, XSS, CSRF, SQL-injection to gain control over the system}
        \item {Implemented mitigation techniques like stack canaries, server-side sandboxing, privilege and access control}
      \end{cvitems}
    }
  \cventry
    {Principles of Database Systems, Prof. Medha Atre}
    {\href{https://github.com/tulsyan/railquery}{RailQuery}}
    {IIT Kanpur}
    {Jan. 2017 - May 2017}
    {
      \begin{cvitems}
        \item {Implemented miniature version of Rail Enquiry using the Neo4j Database with static data obtained from railway API.}
        \item {Designed an \textbf{ANNE stack} based rail enquiry website, using MVC framework, to answer queries like train between stations, train routes, all directly reachable stations, connecting trains using proper DB structure and indices}
      \end{cvitems}
    }
  \cventry
    {Operating Systems, Prof. Mainak Chaudhari}
    {\href{https://bitbucket.org/arhamchopra11/nachos-assignments}{Delving into UNIX with NachOS}}
    {IIT Kanpur}
    {Aug 2016 - Dec 2016}
    {
      \begin{cvitems}
        \item {Implemented some parts of the \textbf{Standard System Call Library} like fork, join, exec, sleep, exit, etc. in NachOS}
          % {Implemented parts of the \textbf{Standard System Call Library}, different \textbf{process scheduling algorithms}, \textbf{virtual memory}, \textbf{dynamic page allocation strategies} and analyzed their effectiveness in different use cases on the NachOS}
        \item {Implemented and evaluated performance of process scheduling algorithms(UNIX, RR, FCFS, etc) in varying workload}
        \item {Implemented the Virtual Memory and different dynamic page allocation strategies of the UNIX Operating System such as LRU, LRU Clock, FIFO, etc. and evaluating the performance of each on varying workload environments}
      \end{cvitems}
    }
  \cventry
    {Summer Project, Robotics Club}
    {\href{https://bitbucket.org/arhamchopra11/voicecommandrecognition}{Voice Command Recognition}}
    {IIT Kanpur}
    {Jun. 2015 - Jul. 2015}
    {
      \begin{cvitems}
        \item {Developed a voice recognition system in Matlab and voice navigated a bot under different noise environments}
        \item {Employed MFCC and DTW algorithm with noise filters to recognize vocal commands and perform actions accordingly}
      \end{cvitems}
    }
  \cventry
    {Other Projects}
    {}
    {}
    {}
    {
      Combining Inpainting with Image Traslation, 
      \href{https://bitbucket.org/arhamchopra11/stockprediction}{Stock Market Prediction}, 
      \href{https://bitbucket.org/arhamchopra11/meetupscheduler}{Meetup Scheduler}, 
      Introduction to Cryptography, 
      % The Pascal's Triangle,
      % The Flying Raptor
    }
\end{cventries}
